Figures

### 2023-03-22 figures/figures.Rmd
label mapview pnts

```{r map}

coords_ire <- sf::st_as_sf(
    data.frame(lat = 50.45055, lon = 4.5350415),
    coords = c("lon", "lat"), crs = 4326)

@@

rmarkdown::render_delayed({
    mapview(dt_sites_close) + mapview(coords_ire, color = "red")
    })
```

>>>>

```{r map}
coords_ire <- sf::st_as_sf(
    data.frame(lat = 50.45055, lon = 4.5350415),
    coords = c("lon", "lat"), crs = 4326)
coords_ire$site_code <- "Fleurus"

@@

m1_data <- dplyr::bind_rows(dt_sites_close, coords_ire)
m1 <- mapview(m1_data)
addStaticLabels(m1, label = m1_data$site_code)
```
